---
title: 'A Maker Project: Creating Dials with R'
author: "David Gabbé"
date: "1/7/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Code to output to different directory:
<!-- knit: (function(inputFile, encoding) {  -->
<!--       out_dir <- 'test'; -->
<!--       rmarkdown::render(inputFile, -->
<!--                         encoding=encoding,  -->
<!--                         output_file=file.path(dirname(inputFile), out_dir, 'analysis.html')) }) -->

## Project Summary

- How to make an attractive speed dial for an upgraded 1947 cast iron drill press.
- add figures & Rpubs text here

## About David

## Credits

Package central to the success of this project so the official cite:

Gu, Z. circlize implements and enhances circular visualization 
  in R. Bioinformatics 2014

## Fonts

- Legibility important for safe operation
- Space contraints need to be solved
- Layout contributes to efficient operation

## Not All Fonts Are Equal `r emo::ji("confounded")`

- Included vs Free vs Paid
- Glyph set
- Encoding
- Format (PostScript Type1, TrueType, Open Font)

## Quartz Fonts

```{r quartz-fonts, echo=TRUE}
quartzFonts()
```

## R Ecosystem

Packages used:

- circlize
- extrafonts
- R.Devices (verify)
- tibble

## References

- [_Circular Visualization in R_](https://jokergoo.github.io/circlize_book/book/), Zuguang Gu
- [_How Big is Your Graph?_](https://rstudio.com/wp-content/uploads/2016/10/how-big-is-your-graph.pdf) Cheat Sheet

## Extra Material

## Measuring Pixels

- [Measuring Pixels](http://blog.pmean.com/measuring-pixels/)
- [Drawing circles](http://blog.pmean.com/circle/)
- [Example of converting between user and device spaces](http://blog.pmean.com/rotating-text/)

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

